### 2024-11-26 skripsi/chapter1.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3

\begin{figure}[h] %h means here!
    \centering
    \includegraphics[width=1.0\linewidth]{figures/snapshot_nasa_airs_aqua_2024_05_21T00_00_00Z.jpg}
    \caption{Daytime and nighttime surface air temperature from observations by the AIRS instrument onboard the NASA AQUA satellite. This shows observations recorded through a whole day on the 21\textsuperscript{st} of May 2024. Notice that parts of the globe, especially near the equator have not been observed. This image was produced using NASA Worldview (\url{https://go.nasa.gov/46SaYyJ}).}\label{fig:satellite_image_coverage}
\end{figure}

@@

Traditional numerical solvers have enjoyed many decades of development due to their long history. There are many general approaches to solve PDEs and many more very specific approaches. Other than FDM, some widely used approaches include Finite Element Methods (FEM), Finite Volume Methods (FVM), Collocation Methods, and Spectral Methods. FEM and FDM are both mesh based approaches, meaning they rely on discretization of the computational domain. There are several challenges associated with this. First, irregular domains such as bio-inspired materials like bone, spider silk, or aggregate materials like gravel pose a challenge due to the complexity of the domain geometry \autocite{gaulSimulationWavePropagation1991,buoniEfficientScalableNumerical2007,jiaModulateStressDistribution2024}. Also, irregular domains which create large deformations or mesh entanglement cause these methods to become ineffective \autocite{chenMeshfreeMethodsProgress2017}. While there are strategies to mitigate this, by definition they are an additional layer of difficulty to the process. Second, multiscale applications where the micro and macro scales are both important require fine meshes such that the small scale structures are adequately simulated. This creates meshes with very large number of points that are very resource intensive \autocite{buoniEfficientScalableNumerical2007}. Third, a single evaluation of traditional mesh-based solvers may not be very costly, however multiple evaluations can add up. This is very apparent in inverse problems where the solver is queried multiple times to solve the forward problem in order to obtain parameter functions. Therefore, in problems where these issues important or resources are limited, mesh-free methods may be preferred. As an example, the spectral method solves PDEs by formulating the solution as a linear combination of global basis functions like the Fourier series. This can be likened to how music combines sound waves of different things to produce the overall sound. The complex formulation of the Fourier series is presented in \lccref{eq:fourier_series}.

@@

\begin{equation}\label{eq:fourier_series}
    s = \sum_{k} c_k e^{2\pi ikx}
The example differential equation we wish to solve is the simple derivative in \lccref{eq:derivative}. In other words, the aim is to find a function \(u^{*} \) from a known function \(f^{*} \). This means we are learning the anti-derivative operator or more loosely known as the integral. To do this we first formulate both into separate Fourier series approximations \(u \) and \(f \) in \lccrefs{eq:example_fourier_1,eq:example_fourier_2} respectively.

@@

    \dv{u^*\left( x \right)}{x} & = f^*\left( x \right) \label{eq:derivative}                                                      \\
    u^*\left( x \right)         & \approx u\left( x \right)         = \sum_{k} \hat{u}_k e^{2\pi ikx} \label{eq:example_fourier_1} \\
    f^*\left( x \right)         & \approx f\left( x \right)         = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_fourier_2}

@@

Next we take the derivative of \lccref{eq:example_fourier_1} which result in \lccref{eq:fourier_series_derivative}. Using this we can substitute the terms in \lccref{eq:derivative} with \lccrefs{eq:fourier_series_derivative,eq:example_fourier_2} giving \lccref{eq:example_spectral_method_fourier_substituted}. Finally, after some algebraic manipulation we obtain \lccref{eq:derivative_coeff}. One also needs to choose \(\hat{u}_{0}\), which is the integration constant. Practically this would be done with a finite number of modes and the coefficients \(\hat{f}_k\) are obtained using a Discrete Fourier Transform (DFT) algorithm like the Fast Fourier Transform (FFT).
    \dv{u\left( x \right)}{x}                                    & = \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} \label{eq:fourier_series_derivative} \\
    \sum_{k} \hat{u}_k\times \left( 2\pi ik \right) e^{2\pi ikx} & = \sum_{k} \hat{f}_k e^{2\pi ikx} \label{eq:example_spectral_method_fourier_substituted}            \\
    \hat{u}_k                                                    & = \hat{f}_k / \left( 2\pi ik \right) \label{eq:derivative_coeff}
The fourth challenge with traditional methods is that they require prior knowledge of analytic forms of PDEs. This is because the solvers use the equations to formulate solutions. This makes traditional numerical approaches unsuited to data dominant problems. These challenges altogether are some of what weather forecasting faces; NWP has the immense task of modeling multiple scales of the Earth's atmosphere while accounting for geographical features of physical systems that are still not fully understood. Many other fields also face these challenges which has motivated research into alternative methods that do not completely rely on prior knowledge, are mesh free, and fast enough when solving forward problems.

@@

\section{Limitations}
\noindent This work is limited to the following:
\begin{enumerate}
    \item Functions the model works with are only continuous functions.
    \item Hardware used in this project is limited to the standard offering on \url{kaggle.com} as of \today{}.
    \item The basis functions are limited to Fourier basis. % TODO: change this if more basis functions are added
    \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.
\end{enumerate}

>>>>

\begin{figure}[ht] %h means here!
    \centering
    \includegraphics[width=1.0\linewidth]{figures/snapshot_nasa_airs_aqua_2024_05_21T00_00_00Z.jpg}
    \caption{Daytime and nighttime surface air temperature from observations by the AIRS instrument onboard the NASA AQUA satellite. This shows observations recorded through a whole day on the 21\textsuperscript{st} of May 2024. Notice that parts of the globe, especially near the equator have not been observed. This image was produced using NASA Worldview (\url{https://go.nasa.gov/46SaYyJ}).}\label{fig:satellite_image_coverage}
\end{figure}

@@

Traditional numerical solvers have enjoyed many decades of development due to their long history. There are many general approaches to solve PDEs and many more very specific approaches. Other than FDM, some widely used approaches include Finite Element Methods (FEM), Finite Volume Methods (FVM), Collocation Methods, and Spectral Methods. FEM and FDM are both mesh based approaches, meaning they rely on discretization of the computational domain. There are several challenges associated with this. First, irregular domains such as bio-inspired materials like bone, spider silk, or aggregate materials like gravel pose a challenge due to the complexity of the domain geometry \autocite{gaulSimulationWavePropagation1991,buoniEfficientScalableNumerical2007,jiaModulateStressDistribution2024}. Also, irregular domains which create large deformations or mesh entanglement cause these methods to become ineffective \autocite{chenMeshfreeMethodsProgress2017}. While there are strategies to mitigate this, by definition they are an additional layer of difficulty to the process. Second, multiscale applications where the micro and macro scales are both important require fine meshes such that the small scale structures are adequately simulated. This creates meshes with very large number of points that are very resource intensive \autocite{buoniEfficientScalableNumerical2007}. Third, a single evaluation of traditional mesh-based solvers may not be very costly, however multiple evaluations can add up. This is very apparent in inverse problems where the solver is queried multiple times to solve the forward problem in order to obtain parameter functions. Therefore, in problems where these issues important or resources are limited, mesh-free methods may be preferred. As an example, the spectral method solves PDEs by formulating the solution as a linear combination of global basis functions like the Fourier series. This can be likened to how music combines different sound waves to produce the overall sound. For some function \(s\), the approximation \(s^*\) gets closer to the original with more linear combinations of basis functions. The complex formulation of the Fourier series is presented in \lccref{eq:fourier_series}. With this approach, the approximated function is characterized completely by its coefficients \(c_k\). This fact is exploited by the spectral method to solve differential equations. The solution function can be approximated by finding the mapping between input function coefficients and solution function coefficients. The mapping between a function \(s\) and its derivative \(s^{\prime}\) can be found using the derivative equation from their coefficients leading to \(\hat{s}_k = \hat{s}^{\prime}_k/\left(2\pi ik\right)\). Practically this would be done with a finite number of coefficients (\(k < \infty \)) and the coefficients \(\hat{s}^{\prime}_k\) are obtained using a Discrete Fourier Transform (DFT) algorithm like the Fast Fourier Transform (FFT).

@@

@@

    s & \approx s^* = \sum_{k} \hat{s}_k e^{2\pi ikx}\label{eq:fourier_series}

@@

This leads us to the fourth challenge with traditional methods which is that they require prior knowledge of analytic forms of PDEs. This is because traditional solvers use the equations to formulate solutions. This makes traditional numerical approaches unsuited to problems where the governing equations are unknown or partially known. These challenges altogether are some of what weather forecasting faces; NWP has the immense task of modeling multiple scales of the Earth's atmosphere while accounting for features of physical systems that are still not fully understood. Many other fields such as epidemiology \autocite{brauerMathematicalModelsEpidemiology2019} and ecology \autocite{holmesPartialDifferentialEquations1994,turchinDoesPopulationEcology2001} also face these challenges. As with many other fields, at some point in time the governing equations of many systems were not known. This has motivated research into alternative methods that do not completely rely on prior knowledge, are mesh free, and fast enough when solving forward problems.

@@

\section{Limitations}
\noindent This work is limited to the following:
\begin{enumerate}
    \item Functions the model works with are only continuous functions.
    \item The basis functions are limited to Fourier basis. % TODO: change this if more basis functions are added
    \item Modeled fields are compact or dense meaning not sparse. Sparse observations or other data are assimilated using other methods.
\end{enumerate}

### 2024-11-26 skripsi/chapter2.tex
rename files to english versions, add data figures for antiderivative, add content on data and computational model, edit parts of ch 1 & 3

@@

\section{Referensi dan Citation}
\noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}. Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}. Atau untuk tiga sumber berarti \cite{kongkanand2006,kresse1999,Leibb1993}.

>>>>

\section{Fourier Transform and Series}
\noindent

Complex numbers are numbers consisting of real and imaginary components. Complex numbers are written as in \lccref{eq:complex_number} with \(a \) and \(b \) being the real and imaginary components respectively. The imaginary component is multiplied by the imaginary unit \(i=\sqrt{-1}\).
\begin{align}
  c = a + bi \label{eq:complex_number} \\
\end{align}

@@

\section{Referensi dan Citation}
% \noindent Sitasi dapat dimasukkan ke dalam Tugas Akhir seperti ini \cite{Fujita1996}. Untuk sitasi dengan beberapa sumber, dapat dituliskan juga \cite{hohen1964,Kim2006}. Atau untuk tiga sumber berarti \cite{kongkanand2006,kresse1999,Leibb1993}.
